% !TEX root = main.tex

\vspace{-0.2cm}

\section{Experimental Design} %Done

\vspace{-0.1cm}
We evaluate the performance of $\DALock$ through an extensive battery of empirical simulations. In this section, we describe the modeling choices we made when designing our experiments. To simulate the authentication ecosystem, we need to simulate honest users' behavior, the authentication server running $\DALock$, and an online attacker. 



Briefly, when simulating users, we need to model the distribution over users’ passwords, the distribution over honest login mistakes (e.g., typos or recall errors), and the user's login schedule. When simulating the distribution over users’ passwords, we use multiple empirical datasets to define the underlying password distribution. We use a Poisson arrival process to model the frequency of user login attempts~\cite{AC:BloBluDat13}. Our model for users’ mistakes is informed by recent empirical studies of password typos~\cite{CCS:CWPCR17,SP:CAAJR16} and is augmented to simulate other mistakes, i.e., recall errors.  The key question for simulating an authentication server running $\DALock$ is how the (password) frequency oracle $\EstP{\cdot}$ is implemented. We consider two concrete implementations: password strength models~\cite{ USENIX:Wheeler16,USENIX:USBCCKKMMS15,USENIX:MUSKBCC16} (e.g., $\ZX$, Markov Models, Neural Networks) and (differentially private) count sketches. When simulating the attacker, we consider an untargeted one who knows the distribution over user passwords as well as the $\DALock$ mechanism --- including the frequency oracle $\EstP{\cdot}$. We leave the question of tuning DALock to protect against targeted online attackers~\cite{CCS:WZWYH16} as an important direction for future research. We elaborate on each of these key model components below.  We begin by with an overview of the empirical datasets $\SampledData{\AllUser}$ that we used in our experiments.




% LinkedIn\cite{Dataset:LinkedIn}, and Yahoo\cite{SP:Bonneau12,NDSS:BloDatBon16}



\vspace{-0.2cm}
\subsection{Experimental Datasets}\label{section:experiment:experiment_dataset} 


In this work, we use multiple real-world password datasets (see Table~\ref{table: datasetsummary}). Those datasets were either hacked or leaked via various vulnerabilities and eventually made public on the Internet. The only exception is the Yahoo dataset, which is a sanitized password frequency dataset collected~\cite{SP:Bonneau12}  with permission from Yahoo!. It consists of anonymized password histograms representing almost 70 million Yahoo! users who logged into their account during a $48$-hour window in May 2011. Yahoo! later authorized the public release of a differentially private version of this dataset~\cite{NDSS:BloDatBon16}. We remark that this frequency corpus \textit{does not contain any plaintext passwords}, so we did not use password strength models in our experiments involving the Yahoo! dataset. In \lazyref{Section}{section:experimentalresult}, we present the result using all datasets except LinkedIn\footnote{The LinkedIn dataset we used is a plaintext password corpus (\textit{partially}) recovered constructed from a leak in 2012. It contains approximately $68$ million cracked passwords, but the actual size of the leak is larger. Furthermore, there is a larger (differentially private) frequency corpus (without plaintext) based on $174+$ million passwords~\cite{harsha2020bicycle} that is publicly available. However, this dataset does not include any plaintext passwords. We chose to use the smaller dataset in our experiments so that we could evaluate with frequency oracles based on password models (e.g., $\ZXCVBN$, PCFGs, Neural Networks).}  and Yahoo. Results on these two datasets can be found in \lazyref{Appendix}{appendix:experimentalResults}.

Each dataset defines an empirical password distribution. In each of our experiments, we assume that this distribution matches the real (unknown) password distribution from which these datasets were sampled. While the empirical distribution may not precisely match the real one, we stress that our analysis focuses on the most popular passwords in the distribution --- the ones that an attacker will try to guess. Because the datasets are all quite large ( the smallest dataset has over $0.5$ million passwords), standard concentration bounds imply that the true probability of a popular password in the distribution will almost certainly closely match the empirical probability.

% In our experiments we assume that the empirical distribution We assume each dataset (approximately) reflects the actual distribution due to their tremendous size. To ease the presentation, we refer ``actual distribution" to the datasets mentioned in this section. We do acknowledge there could be misalignment between datasets and their true underlying distributions (e.g., partial leakage). Nevertheless, we focus on analyzing popular passwords where empirical distribution and real distribution will be very similar. 





%\textbf{RockYou}\cite{Dataset:RockYou} is a plaintext password corpus contains 14,341,564 unique passwords from a data leakage in 2009. RockYou stored user data in unencrypted database and leaked the passwords due to SQL-injection attacks. %To the best of our knowledge, RockYou is the largest leaked dataset with \textit{plaintext} passwords. 



%\textbf{LinkedIn}\cite{Dataset:LinkedIn} is a plaintext password corpus (partially) recovered constructed from a leakage in 2012. While the passwords were originally hashed LinkedIn was using a weak (unsalted) password hashing algorithm and almost all of the passwords in the dataset have been cracked. The dataset we used has approximately $68$ million passwords. We remark that the actual size of the leak is larger and that there is a larger (differentially private) frequency corpus based on $174+$ million LinkedIn passwords~\cite{harsha2020bicycle} that is publicly available. 



% Notice that the actual leakage is larger, but we choose to use this version because the plaintexts are available to us.   % This is the plaintext version



%\textbf{Yahoo!} 




\vspace{-0.2cm}
\begin{table}[h]
	
	
	\scalebox{1.05}{
		
		
		\begin{tabular}{|c|c|c|c|c|}
			
			
			\hline
			
			
			Dataset     & Passwords & Accounts & $\TrueP{pw_1}$ & $\TrueP{pw_{1-10}}$ \\ \hline
			
			
			Yahoo    & 33,895,873                     &  69,301,337            & 1.1\%  & 1.9\%                \\ \hline
			
			RockYou  & 14,341,564                & 32,603,388                      & 0.89\%  &2.1\%                   \\ \hline
			
			000webhost  & 10,587,915               & 14,960,642                      &  0.081\%&0.48\% \\ \hline
			
			LinkedIn&  6,840,885              & 68,361,064                    &1.53\% &2.82\%                        \\ \hline
			CSDN  & 4,037,268               & 5,908,494                       & 1.29\%     &3.72\%               \\ \hline
			
			clixsense  & 1,628,297               & 2,195,900 &  0.15\% & 0.7\% \\ \hline
			
			brazzers & 587,934 & 925,614 &0.58\% &1.13\%\\ \hline
			
			bfield  & 416,034& 539,434&  0.48\% & 1.97\% \\ \hline
			
			
		\end{tabular}
		
		
	}
	\vspace{-0.1cm}
	
	\caption{Summary of dataset}\label{table: datasetsummary}
	
	
\end{table}

\vspace{-0.3cm}


\mypara{Ethics:} The datasets we used contain passwords that were previously stolen and subsequently leaked online. The use of such data raises critical ethical considerations; however, such password lists are already publicly available online, so our use of the data does not exacerbate the prior harm to users. We did not crack any new user passwords. Furthermore, the datasets we use have been cleaned of all identifying information beyond the passwords themselves.  In summary, we believe that our use of the leaked data will not exacerbate prior harm to users, and the lockout mechanism we develop and evaluate may help to protect user passwords in the future.





%\mypara{Subsampling Datasets} %\done We construct the subsampling datasets due to the incentives mentioned in \textbf{Section}~\ref{section:ExperimentDesign-subsection:SimulateServer}. To simulate the case of partial participation, we build datasets $\SampledData{\AllUser_{r\%}}$ by subsampling r\% of the users from actual distribution. For the rest of the discussion, we refer such obtained datasets to ``sampled datasets" and denote them with $\SampledData{\AllUser_{r\%}}$. In this experiment, we assume the server stores the sampled distribution, but the activities of attackers and users are simulated based on the actual distribution. 



%In this work we demonstrate the results of using sampling rate 1\%, 5\%, and 10\%. We show that even $\sigma_{1\%}$,  $\CountSketch$ trained on $\SampledData{\AllUser_{1\%}}$, can be as effective as $\sigma$. 





%\mypara{Banning Popular passwords} %\done


%Banning weak passwords is a orthogonal approach to eliminate over-popular passwords as we mentioned earlier. To test the performance of $\DALock$ under such circumstance, we construct new dataset by banning top 10,000 passwords from the origin dataset. Notice that we assume that users who are affected by banning will choose new passwords based on the remaining distribution. The reason for reassigning passwords is to ensure that the total number of users stays the same. 





% In our simulations we assume that the attacker can access the same frequency oracle used by $\DALock$. For simplicity we also assume that the attacker can foresee the times at which an honest user will login and/or make mistakes and optimize his guessing pattern accordingly. In particular, the attacker might try to exploit passwords whose true popularity have been underestimated by the popularity estimator. We show that $\DALock$ implemented by all estimator can be effective. 
\vspace{-0.2cm}
\input{ModelingUsers}
\vspace{-0.2cm}
\input{ModelingAuthenticationServer}


%Done



\input{ModelingAttacker}



